---
title: "Registered Pets"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    source_code: embed
    theme: lumen
    vertical_layout: fill
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE, 
  warning = FALSE, 
  message = FALSE
)
```

<!----
```{r input_demo, eval=FALSE}
# input <- list(
#   age_group = "0 - 5"
# )
```
---->
 
```{r workspace}
library(tidyverse)
library(glue)
library(DT)            # datatable
library(flexdashboard) # valueBox
library(scales)        # percent, comma
library(plotly)        # ggplotly
library(simplecolors)  # sc
library(shinyWidgets)  # radioGroupButtons
library(shiny)         # sliderInput

animals <- read_rds("registered_animals.Rds")

color_dogs <- sc("blue3")
color_cats <- sc("teal3")
```

```{r functions}
nice_datatable <- function(df, caption = NULL, ...) {
  df %>%
    datatable(
      extensions = c("Buttons", "FixedHeader", "Scroller"),
      filter = "top",
      rownames = FALSE,
      escape = FALSE,
      caption = caption,
      options =
        list(
          dom = "Brtip",
          deferRender = FALSE,
          scrollY = 300,
          scroller = TRUE,
          scrollX = TRUE,
          fixedHeader = FALSE,
          buttons = c("copy", "csv", "excel", "pdf", "print"),
          pageLength = nrow(df),
          lengthChange = FALSE,
          ...
        )
    )
}
```

STATS
==========================

Sidebar {.sidebar data-width=220}
--------------------------

```{r age_input}
age_groups <- as.character(sort(unique(animals$age_group)))

shinyWidgets::radioGroupButtons(
  inputId = "age_group",        # < - input$age_group--------
  label = "Select Age Group:",
  choices = c("All", age_groups),
  selected = "All",
  direction = "vertical",
  justified = TRUE,
  width = "150px" 
)

shiny::sliderInput(
  inputId = "n",                 # < - input$n --------------
  label = "# of Results:",
  min = 1,
  max = 20,
  value = 10
)

filtered_data <- reactive({ # < - filtered_data() -------
  if (input$age_group != "All") {
    filter(animals, age_group %in% input$age_group)
  } else {
    animals
  }
})

```


This data comes from [The Sunshine Coast Council](https://data.sunshinecoast.qld.gov.au/Administration/Registered-Animals/7f87-i6kx/data # http://rstudio-pubs-static.s3.amazonaws.com/434674_24af082031324d9c8e8739d1ca7227f9.html) in Queensland, Australia (10/1/2020).

A demo analysis can be found [here](http://rstudio-pubs-static.s3.amazonaws.com/434674_24af082031324d9c8e8739d1ca7227f9.html)

Row {data-height=100}
-------------------

###

```{r}
renderValueBox({
 df <- filtered_data()
  
  flexdashboard::valueBox(
    value = comma(nrow(df)),
    caption = "registered pets",
    icon = "fas fa-paw",
    color = "grey"
  )
})
```

###
```{r}
valueBox(                                                # < --------
  value = percent(mean(animals$sterile)), 
  caption = "spayed/neutered",
  icon = "fa-hand-scissors",
  color = "grey"
)
```

###
```{r}
valueBox(                                                # < --------
  value = comma(sum(animals$species == "Cat")),
  caption = "Cats",
  color = color_cats
)
```

###
```{r}
valueBox(                                                # < --------
  value = comma(sum(animals$species == "Dog")),
  caption = "Dogs",
  color = color_dogs
)
```


Row
--------------------

###

```{r datatable}
DT::renderDataTable({
  df <-
    filtered_data() %>% 
    count(gender, species, name, sort = TRUE) %>% 
    group_by(gender, species) %>%
    mutate(Rank = row_number()) %>% 
    ungroup() %>% 
    filter(Rank <= 10) %>%                              # < --------
    mutate(name = glue::glue("{name} ({n})")) %>% 
    select(-n) %>% 
    pivot_wider(
      names_from = c(gender, species),
      names_sep = "-", 
      names_sort = TRUE,
      values_from = name
    )
  
  nice_datatable(df, caption = glue("Top {10} Pet Names")) # < --------
})


```

### Top Breeds

```{r plot}
plotly::renderPlotly({
  p <-
    filtered_data() %>%
    group_by(species) %>% 
    mutate(
      breed = 
        fct_lump_n(breed, 10) %>%                        # < --------
        fct_infreq() %>% 
        fct_rev()
    ) %>% 
    ungroup() %>% 
    filter(breed != "Other") %>% 
    ggplot(aes(y = breed, fill = species)) +
    geom_bar() +
    facet_wrap(~ species, scales = "free") +
    scale_fill_manual(values = c(color_cats, color_dogs)) +
    theme_minimal() +
    theme(
      panel.grid = element_blank(),
      legend.position = "none"
    ) +
    labs(
      x = "# of Pets",
      y = NULL,
      fill = NULL
    )
  
  plotly::ggplotly(p)
})
```


BELLAS
==========================

```{r bella_table}
animals %>%
  filter(str_detect(name, "Bella")) %>%
  select(
    species, age_group, age, breed, breed_specific, locality, sterile
  ) %>%
  mutate_if(is.factor, fct_drop) %>%
  rename_all(~str_replace_all(toupper(.x), "_", " ")) %>% 
  nice_datatable(caption = "All the Bellas")
```

YOUR TURN
==========================

Column
--------------------------
### Needs Fixing
* valueboxes for cat & dog totals should be reactive
* top names should be reactive to `input$n`
* plot of breeds should be reactive to `input$n`
* add a toggle for cats vs dogs
* **Questions**
  * What breed is the oldest Bella?
  * What is the most common suffix in the top 13 spot?
  * How many cats are 15+?

### more ideas
* turn the table + plot into a [tabset](https://rmarkdown.rstudio.com/flexdashboard/using.html#tabsets)
* change the [theme](https://rmarkdown.rstudio.com/flexdashboard/using.html#appearance)
* most popular gender neutral names
* what names are most popular for unpopular breeds
* can you make the Bella's table reactive
* can you replace the 2nd valuebox with a new plot?
* play around :)
* Upload pictures [here](https://drive.google.com/drive/folders/1NqUKWiYBsroxDYlUliB6_bdh4YKE94jO?usp=sharing)

Column
--------------------------
### Tutorials
* `flexdashboard` - [tutorial](https://rmarkdown.rstudio.com/flexdashboard/using.html#layout)
* `shinyobjects` - [tutorial](https://rjake.github.io/shinyobjects/)
* `shinyWidgets` - demo [here](https://dreamrs-vic.shinyapps.io/shinyWidgets/) and docs  [here](https://dreamrs.github.io/shinyWidgets/index.html)



```{r end}
knitr::knit_exit() # stops knitting at this point
```

# fontawesome
```{r}
search_fonts <- function(pattern) {
  fontawesome:::fa_tbl %>% 
    select(-svg) %>%
    filter(str_detect(name, pattern))
}

search_fonts("paw")
# search_fonts("cat")
# search_fonts("dog")
search_fonts("scissor")
```




























*ANSWERS* *****************************
- What Breed is the oldest Bella? *labrador*
- Wha is the most common suffix in the top 13 spot? *-ly*
- How many cats are 15+? *385*
