---
title: "Registered Pets"
output: html_document
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE, 
  warning = FALSE, 
  message = FALSE
)
```

```{r input_demo, eval=FALSE}
input <- list(
  age_group = "0 - 5"
)
```

```{r workspace}
library(tidyverse)
library(DT)           # datatable

animals <- read_rds("registered_animals.Rds")

```

This data comes from [The Sunshine Coast Council](https://data.sunshinecoast.qld.gov.au/Administration/Registered-Animals/7f87-i6kx/data # http://rstudio-pubs-static.s3.amazonaws.com/434674_24af082031324d9c8e8739d1ca7227f9.html) in Queensland, Australia (10/1/2020).

A demo analysis can be found [here](http://rstudio-pubs-static.s3.amazonaws.com/434674_24af082031324d9c8e8739d1ca7227f9.html)

### Top 10 Pet Names

```{r age_input}
age_groups <- as.character(sort(unique(animals$age_group)))

shinyWidgets::radioGroupButtons(
  inputId = "age_group",
  label = "Select Age Group:",
  choices = c("All", age_groups),
  selected = "All"
)
```

```{r datatable}
DT::renderDataTable({
  df <-
    animals %>%
    filter(age_group %in% input$age_group | input$age_group == "All") %>% 
    count(gender, species, name, sort = TRUE) %>% 
    group_by(gender, species) %>%
    mutate(Rank = row_number()) %>% 
    ungroup() %>% 
    filter(Rank <= 10) %>% 
    mutate(name = glue::glue("{name} ({n})")) %>% 
    select(-n) %>% 
    pivot_wider(
      names_from = c(gender, species),
      names_sep = "-", 
      names_sort = TRUE,
      values_from = name
    )
  
  DT::datatable(
    df,
    filter = "top",
    rownames = FALSE,
    options = list(dom = "i")
  )
})


```

### Top Breeds

```{r plot}
# <h2 style="font-size:50px">&#128049&#128054;</h2>

plotly::renderPlotly({
  p <-
    animals %>% 
    filter(age_group %in% input$age_group | input$age_group == "All") %>%
    group_by(species) %>% 
    mutate(
      breed = 
        fct_lump_n(breed, 10) %>% 
        fct_infreq() %>% 
        fct_rev()
    ) %>% 
    ungroup() %>% 
    filter(breed != "Other") %>% 
    ggplot(aes(y = breed)) +
    geom_bar(fill = "dodgerblue") +
    facet_wrap(~ species, scales = "free") +
    theme_minimal() +
    theme(
      panel.grid = element_blank(),
      legend.position = "none"
    ) +
    labs(
      x = "# of Pets",
      y = NULL,
      fill = NULL
    )
  
  plotly::ggplotly(p)
})

knitr::knit_exit() # stops knitting at this point
```

# more ideas
* gender neutral names
* what names are most popular for unpopular breeds/colors "(other)"
* most popular name by year of birth
* is there a difference in top names for pets that have been spayed/neutered


# Layouts
https://rmarkdown.rstudio.com/flexdashboard/using.html#tabsets

# Widgets to try
You can view shinyWidgets [here](https://dreamrs-vic.shinyapps.io/shinyWidgets/) [docs](https://dreamrs.github.io/shinyWidgets/index.html)

```{r}
shiny::sliderInput(
  inputId = "age_group",
  label = "Select year of birth:",
  min = min(animals$year_born),
  max = max(animals$year_born),
  value = max(animals$year_born),
  sep = "",
  animate = TRUE
)

```

