---
title: "Flexdashboard Demo"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    source_code: embed
    theme: lumen
    vertical_layout: fill
runtime: shiny
---

```{r input_demo, eval = FALSE}
# this chunk doesn't run but works to troubleshoot reactive data
# helpfulness is enhanced with shinyobjects
input <- list(
  displ = c(2, 5),
  year = 2008
)
```

```{r setup}
library(tidyverse)
library(shiny)        #renderPlot, renderTable, sliderInput
library(shinyWidgets) #radioGroupButtons
raw_data <- mpg 
```

MPG Example
=====================================
Column {.sidebar data-width=200} 
-------------------------------------
Filter the data:

```{r filters}
# You can make this sidebar global by putting it ahead of Tab 1
# below are 2 input options: a gorup of buttons, and a slider

radioGroupButtons( # for categorical variables
  inputId = "year", # this will allow the selection to be referenced as input$cyl
  label = "Select Year of Vehicle", # NULL if you don't want a header
  choiceNames = c("All", sort(unique(raw_data$year))), # can use paste, etc to make nicer display
  choiceValues = c("All", sort(unique(raw_data$year))), # values in the data, need to line up with above
  justified = TRUE, # will fill the width of the container it sits in (sidebar)
  status = "primary"
)

sliderInput(
  inputId = "displ", # referenced as input$displ
  label = "Select Engine Displacement:",
  value = range(raw_data$displ), # default selection, you can move the range around
  min = (min(raw_data$displ)),
  max = (max(raw_data$displ)),
  step = 0.1
)

# This will build a dataframe to use throughout the dashboard. To reference this dataframe, you will need to be in some reactive element ex: renderText({nrow(use_data())}). This is essentially a function and so you will need to use parentheses at the end like this: use_data()

use_data <- reactive({
  df <-
    raw_data %>%
    filter(between(displ, min(input$displ), max(input$displ)))
  
  # this if statement will filter for the selection of the radioGroupButtons
  if (input$year != "All") {
    df <- df %>% filter(year == input$year)
  }
  
  df
})
```

Column {data-width=450}
-----------------------------------------------------------------------
### Highway MPG by Engine Displacement
```{r mpg_plot}
renderPlot({ # renderPlot is only required becuase we are referencing someting reactive: use_data(). Otherwise we could just use ggplot(raw_data,...)
  ggplot(use_data(), aes(displ, hwy)) +
    geom_smooth(color = "grey65") +
    geom_point(aes(color = factor(cyl))) +
    ylim(0, 45) +
    labs(color = "Cylinder") +
    theme(legend.position = "bottom")
})
```

Column
-----------------------------------------------------------------------
### Top 10 by hwy
```{r top_10, fig.height = 5.5}
#this will display a top 10 table that is filtered based on the selections above
renderTable({ # use {...} for the output (an expression)
    use_data() %>%
      arrange(desc(hwy)) %>%
      slice(1:10) %>%
      mutate(Rank = row_number()) %>%
      select(Rank, year, manufacturer, model, trans, hwy, fl, class)
  },
  # renderTable takes additional arguments after the {...}
  spacing = "xs",
  align = "l",
  bordered = TRUE
)
```

### `r renderText({paste("Max Highway MPG by Class in Year:", input$year)})`

```{r by_class, fig.height = 4.5}
# above: using `r ...`  will allow you to run R code outside of a chunk. Here the title is reactive to the year selected

renderTable({ # you can make separate objects (similar to in a function)
  count_n <-
    use_data() %>%
    group_by(class) %>%
    summarise(
      n = n(),
      hwy = max(hwy)) %>%
    ungroup() %>%
    arrange(desc(hwy)) %>%
    select(hwy, class, `#` = n)
  },
  spacing = "xs",
  align = "l",
  bordered = TRUE
)
```

Your Turn
=====================================

Column 
-------------------------------------

### To-Do

The goal of this demo is to understand why each piece of code exists. Some of it is `tidyverse` manipulation, much of it is reactive `shiny` content.  Try to understand what each step does, and how to manipulate it, then work through the list below to make changes to the dashboard. 

**MPG Example**

* Convert the two table display into 2 tabs
* Change buttons to vertical display using `mpg$trans` instead of `mpg$year`
* Change slider to `mpg$hwy`

**This Page**

* Use the `ggplot2::diamonds` dataset
* Build a dashboard  w/ at least 4 widgets/plots (look into `shinyWidgets`)
* Change the title of this page


### Resources

* Find more information about flexdashboards here:
    https://rmarkdown.rstudio.com/flexdashboard/using.html#overview
* The `shinyWidgets` gallery has some nice widgets for filtering:
    https://dreamrs-vic.shinyapps.io/shinyWidgets/
    The gallery isn't always available. Another overview can be found here:      
    https://dreamrs.github.io/shinyWidgets/index.html
* `shinyobjects` can be used for debugging, leard more here
    https://rjake.github.io/shinyobjects/
    
Column {.tabset}
-------------------------------------
   
### Tab 1

```{r tab_1}
```   
 
### Tab 2

```{r tab_2}
```
